---
title: "9_Journals_additional_info"
author: "zuzannazagrodzka"
date: "2023-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This script creates a figure showing how many journals per category (for-profit OA, for-profit noOA, not-for-profit OA and not-for-profit noOA) are owned by the societies, different institutions (other) or solely by publishers.


```{r, message=FALSE}
# Clearing R
rm(list=ls())

# Loading libraries
# Libraries used for text/data analysis
library(tidyverse) 
library(dplyr)
library(tidytext)

# Libraries used to create plots
library(ggplot2)
library(RColorBrewer)

# Library to create a table when converting to html
library("kableExtra") 

# Library to read an arrow file
library(arrow)

```


Importing data

```{r}
# Importing dataset that we originally created and used in our analysis
df_corpuses <- read_feather(file = "./data/original_dataset_reproducibility_check/original_cleaned_data.arrow")

```

# Adding a column profit and access

Adding column based on the name of the journal if its OA run by for profit or not-for-profit: 

- for_profit_no_oa:
"BioSciences", "Biological Conservation", "Conservation Biology", "Ecological Applications","Ecology Letters", "Ecology", "Frontiers in Ecology and the Environment", "Global Change Biology", "Journal of Applied Ecology", "Nature Ecology and Evolution", "Trends in Ecology & Evolution"

- no_profit_no_oa:
"American Naturalist", "Annual Review of Ecology Evolution and Systematics", "Evolution", "Philosophical Transactions of the Royal Society B", "Proceedings of the Royal Society B Biological Sciences"

- for_profit_oa:
"Arctic, Antarctic, and Alpine Research", "Biogeosciences", "Conservation Letters", "Diversity and Distributions", "Ecology and Evolution", "Evolutionary Applications", "Neobiota", "PeerJJournal"

- no_profit_oa:
"Ecology and Society", "Evolution Letters", "Frontiers in Ecology and Evolution", "Plos Biology", "Remote Sensing in Ecology and Conservation", "eLifeJournal"



# Data Prep and Cleaning

``` {r}
# Data preparation

## Getting a data set with the words
data_journals <- df_corpuses

dim(data_journals)
colnames(data_journals)
unique(data_journals$org_subgroups)
# Merging and removing duplicates
data_journals <- data_journals %>% 
  rename(document = name) %>% 
  select(document, org_subgroups) %>% 
  distinct(document, .keep_all = TRUE) %>% 
  filter(org_subgroups %in% c("journals_nonOA", "journals_OA")) %>% 
  rename(access = org_subgroups)

data <- data_journals

# Adding a column with a new variable "profit access"
data$profit_access <- data$document

data$profit_access[data$profit_access%in% c("BioSciences", "Biological Conservation", "Conservation Biology", "Ecological Applications","Ecology Letters", "Ecology", "Frontiers in Ecology and the Environment", "Global Change Biology", "Journal of Applied Ecology", "Nature Ecology and Evolution", "Trends in Ecology & Evolution")] <- "for_profit_no_oa"

data$profit_access[data$profit_access%in% c("American Naturalist", "Annual Review of Ecology Evolution and Systematics", "Evolution", "Philosophical Transactions of the Royal Society B", "Proceedings of the Royal Society B Biological Sciences")] <- "no_profit_no_oa"

data$profit_access[data$profit_access%in% c("Arctic, Antarctic, and Alpine Research", "Biogeosciences", "Conservation Letters", "Diversity and Distributions", "Ecology and Evolution", "Evolutionary Applications", "Neobiota", "PeerJJournal")] <- "for_profit_oa"

data$profit_access[data$profit_access%in% c("Ecology and Society", "Evolution Letters", "Frontiers in Ecology and Evolution", "Plos Biology", "Remote Sensing in Ecology and Conservation", "eLifeJournal")] <- "no_profit_oa"

check <- data

check <- check %>%
  select(profit_access) %>%
  group_by_all() %>%
  summarise(COUNT = n())
check

data_journals <- data

# Adding a column "profit"

data$profit <- data$profit_access

data$profit[data$profit_access%in% c("for_profit_no_oa", "for_profit_oa")] <- "profit"

data$profit[data$profit_access%in% c("no_profit_no_oa", "no_profit_oa")] <- "no_profit"

# # Check that all rows were replaced

check <- data

check <- check %>%
  select(profit) %>%
  group_by_all() %>%
  summarise(COUNT = n())
check

data_journals <- data


```

```{r}
# Adding a column with a new variable "society_journal" that tells us if the journal is run by societies/other organisations or just by publisher

data <- data_journals
data$society_journal <- data$document

data$society_journal[data$society_journal%in% c("BioSciences", "Conservation Biology", "Ecological Applications", "Ecology", "Frontiers in Ecology and the Environment", "Journal of Applied Ecology", "American Naturalist", "Evolution", "Philosophical Transactions of the Royal Society B", "Proceedings of the Royal Society B Biological Sciences", "Conservation Letters", "Ecology and Evolution", "Evolution Letters", "Remote Sensing in Ecology and Conservation")] <- "yes"


data$society_journal[data$society_journal%in% c("Biological Conservation", "Global Change Biology", "Nature Ecology and Evolution", "Trends in Ecology & Evolution", "Annual Review of Ecology Evolution and Systematics", "Diversity and Distributions", "Evolutionary Applications", "PeerJJournal", "Ecology and Society", "Frontiers in Ecology and Evolution", "Plos Biology", "eLifeJournal")] <- "no"


data$society_journal[data$society_journal%in% c("Ecology Letters", "Arctic, Antarctic, and Alpine Research", "Biogeosciences", "Neobiota")] <- "other"


# Check that all rows were replaced

check <- data

check <- check %>%
  select(society_journal) %>%
  group_by_all() %>%
  summarise(COUNT = n())
check

data_journals <- data

```


```{r}
# Data prep for the figure
head(data_journals)
# calculate percentages, put into dataframe
df <- data_journals %>%
  mutate(access = factor(access)) %>% 
  mutate(profit_access = factor(profit_access)) %>%
  mutate(profit = factor(profit)) %>%
  mutate(society_journal = factor(society_journal)) %>%
  group_by(profit_access, society_journal) %>%
  summarize(n = n()) %>%
  mutate(freq = n / sum(n))

df
```


Creating a figure


```{r}

legend_title <- "Society-owned"

ggplot(df, aes(x = profit_access, y = n, fill = society_journal)) +
  geom_bar(stat='identity') +
  theme_bw() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +
  scale_fill_manual(legend_title, values=c("#999999", "#E69F00", "#56B4E9")) + #no, other, yes
  scale_x_discrete(limit = c("for_profit_no_oa", "for_profit_oa", "no_profit_no_oa", "no_profit_oa"),
                     labels = c("For-profit nonOA","For-profit OA","Non-profit nonOA", "Non-profit OA")) +
  labs(y= "Frequency", x = "Journal category")
  
```



