---
title: "Compare_datasets"
author: "zuzannazagrodzka"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Comparing datasets

This code is used to compare a dataset that we originally generated and the one that will be produced in "1a_Data_preprocessing" file. The results will be reproducible in the next steps only if the datasets are identical, otherwise, the topic modeling will generate different topics. 

# Loading libraries

```{r}
library(arsenal) # for dataset comparison

```


# Importing datasets

```{r}
# Importing original dataset
original_data <- read.csv(file = "./data/original_dataset_reproducibility_check/original_cleaned_data.csv")
original_data <- original_data[order(word),]
dim(original_data)

# Importing a dataset I want to check 
test_data <- read.csv(file = "./output/created_datasets/cleaned_data.csv")
dim(test_data)
```

# Comparing datasets

```{r}
comparedf(original_data, test_data, by="word")
summary(comparedf(original_data, test_data, by="word"))
```

# Session information

```{r}
sessionInfo()
```
