---
title: "Figure_2A"
author: "ZZ, APB, TFJ"
# author: "zuzannazagrodzka"
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating Figure 2A

Figure 2A shows gamma values (x-axis, means ± sd) that are the strength of association between a set of stakeholder documents (y-axis) and the corresponding topic. 

High gamma values are strong associations. 

We plotted the values for four main topics (side labels): Open Research (green), Community and Support (red), Innovation and Solutions (yellow) and Publication Process (blue). 

The data for this are produced in `2_Topic_modeling`

# R Setup and packages

```{r Cleaning R}
rm(list=ls())
```

# Libraries
``` {r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

# Import data to create Figure 2A

The data are produced in `2_Topic_modeling`

``` {r}
# Importing data produced in "2_Topic_modeling.Rmd"

# df_doc_level_stm_gamma <- read_csv(file = "./output/created_datasets/df_doc_level_stm_gamma.csv")

# Importing data that we originally created and used in our analysis
df_doc_level_stm_gamma <- read.csv(file = "./data/original_dataset_reproducibility_check/original_df_doc_level_stm_gamma.csv")
```

# Data management

``` {r}
# glimpse(df_doc_level_stm_gamma)
# head(df_doc_level_stm_gamma, 10)

df_figure1_gamma <- df_doc_level_stm_gamma %>% 
  select(-total_topic, -total_sent) 

df_figure1_gamma$prop <- df_figure1_gamma$prop *100

df_figure1_gamma_wide <- df_figure1_gamma %>% 
  spread(topic, prop) %>% 
  rename(topic_1 = `1`, topic_2 = `2`, topic_3 = `3`, topic_4 = `4`)


# Topic/Category 1: Open Research 
# Topic/Category 2: Community & Support
# Topic/Category 3: Innovation & Solution
# Topic/Category 4: Publication process (control)

df_figure1_gamma_wide2 = data.frame(
  document = rep(df_figure1_gamma_wide$name,4),
  stakeholder = rep(df_figure1_gamma_wide$stakeholder,4),
  # type = c(rep("Topic 1",129), rep("Topic 2",129), rep("Topic 3",129), rep("Topic 4", 129)),
    type = c(rep("1. Open Research",129), rep("2. Community and Support",129), rep("3. Innovation and Solutions",129), rep("4. Publication Process", 129)),
  perc = c(df_figure1_gamma_wide$topic_1, df_figure1_gamma_wide$topic_2, df_figure1_gamma_wide$topic_3, df_figure1_gamma_wide$topic_4),
  perc2 = c(df_figure1_gamma_wide$topic_1, df_figure1_gamma_wide$topic_2, df_figure1_gamma_wide$topic_3, df_figure1_gamma_wide$topic_4)
)

# adding quantiles values
sum_figure1_gamma_wide2 = 
  df_figure1_gamma_wide2 %>%
  group_by(stakeholder, type) %>%
  dplyr::summarize(lower = quantile(perc, probs = .25), upper = quantile(perc, probs = .75), perc_fin = mean(perc)) %>% 
  rename(perc = perc_fin)


```

# Graph production

``` {r}

figure_topics <- ggplot() +
  geom_point(data = df_figure1_gamma_wide2, aes(x = perc, y = stakeholder, colour = type), alpha = 0.2, position = position_jitter(), show.legend = FALSE) +
  geom_pointrange(data = sum_figure1_gamma_wide2, aes(x = perc, xmin = lower, xmax = upper, y = stakeholder, colour = type), show.legend = FALSE) +
  facet_grid(.~type) + 
  labs(x = "Topics occuring in documents (%) gamma", y = "") +
  scale_color_manual(values = c("dark green", "dark red", "darkgoldenrod", "dark blue")) +
  theme_classic()

figure_topics

# # UNCOMMENT TO SAVE FIGURES

# figure_name <- paste0("./output/Figure_2A/Figure_2A.png")
# png(file=figure_name,
#   width= 3000, height= 2000, res=400)
#   figure_topics
#   dev.off()

```

# Session information
``` {r}
sessionInfo()
```
